---
output:
  html_document: default
  pdf_document: default
---
|                                                                  |
|------------------------------------------------------------------|
| title: STAT 352  |
| title: Computing Binomial probabilities in R LAB |
| author: "Anna Panorska"                                          |
| output:                                                          |
| html_document:                                                   |
| df_print: paged                                                  |

NOTE: This file contains some R work to get acquainted with R. 


```{r}
library(broom) 
library(lattice)
library(MASS)
``` 
 
Create 5 random observations from Bin(10, 0.5) and compute their probabilities. 

```{r}

dat<- rbinom(5, 10, 0.5) #creating the data
cat("Observations:", dat, "\n") # this command prints to the screen
dat #looking at the data

#Computing probabilities:

binprob<-dbinom(dat, 10, 0.5)
cat("Probabilities:", binprob, "\n")
binprob
```

Suppose X has a binomial distribution with the number of trials 20 and probability of success 0.2. Find the following probabilities: 
$P(X = 10), P(X = 2), P(X = 5), P(X \leq 3), P( X < 3), P( X > 3), P(X \geq 3), P( 2 < X \leq 7), P(2 \leq X \leq 7), 
P(2 \leq X < 7), P(2 < X < 7)$.

```{r}
#P(X = 10)

p1<-dbinom(10, 20, 0.2)
cat("P(X = 10)=", p1, "\n")
cat("\n") # empty line in the output
#P(X = 2)

dbinom(2, 20, 0.2)
p2<-dbinom(2, 20, 0.2)
cat("P(X = 2)=", p2, "\n")
cat("\n")

#P(X = 5)

dbinom(5, 20, 0.2)
p3<-dbinom(5, 20, 0.2)
cat("P(X = 5)=", p3, "\n")

cat("\n")

#P(X \leq 3) 
# For this calculation we can add individual probabilities of 0, 1, 2, and 3, OR use pbinom function in R

cat("Summing probs we get:", "\n")
dbinom(0, 20, 0.2)+dbinom(1, 20, 0.2)+dbinom(2, 20, 0.2)+dbinom(3, 20, 0.2)

cat("Using the pbinom we get:", "\n")
pbinom(3, 20, 0.2, lower.tail=TRUE)

# P( X < 3) = P(X <= 2)
pbinom(2, 20, 0.2, lower.tail=TRUE)

# P( X > 3)
pbinom(3, 20, 0.2, lower.tail=FALSE)

# P( 2 < X <= 7) = P(X <= 7) - P(X <= 2)
pbinom(7, 20, 0.2, lower.tail=TRUE) - pbinom(2, 20, 0.2, lower.tail=TRUE)

# P(2 <= X <= 7) = P(X <= 7) - P(X < 2) = P(X <= 7) - P(X <= 2) + P(X = 2), or
# P(2 <= X <= 7) = P(X <= 7) - P(X <= 1)
pbinom(7, 20, 0.2, lower.tail=TRUE) - pbinom(2, 20, 0.2, lower.tail=TRUE) + dbinom(2, 20, 0.2)
pbinom(7, 20, 0.2, lower.tail=TRUE) - pbinom(1, 20, 0.2, lower.tail=TRUE)

# P(2 <= X < 7) = P(X < 7) - P(X < 2) = P(X <= 6) - P(X <= 1)
pbinom(6, 20, 0.2, lower.tail=TRUE) - pbinom(1, 20, 0.2, lower.tail=TRUE)

# P(2 < X < 7) = P(X < 7) - P(X <= 2) = P(X <= 6) - P(X <= 2)
pbinom(6, 20, 0.2, lower.tail=TRUE) - pbinom(2, 20, 0.2, lower.tail=TRUE)
```
